Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-04 src/paper.tex
update

The encoding strategy on the mixed speech plays a pivotal role in the model performance. Assume we 
have a reference speech \(s_r \in R^{T^r} \) and mixed speech \(s \in R^{T'}\). 
We follow the 
aforementioned procedure for 
reference speech to get tensor \(\bm{d_r}\) of shape \(n \times T_r\). But for the mixed 
speech, instead of directly following the procedure, we first concatenate it with 
the reference speech to get \(s' = [s_r, s_m, s_r] \in R^{(T^r+T'+T^r)}\). Then we use this speech 
as input for the encoder, obtaining output \(d'\) of shape \(n \times \)

>>>>

The encoding strategy on the mixed speech plays a pivotal role in the model performance. Assume we 
have a reference speech \(s_r \in R^{T^r} \) and mixed speech \(s \in R^{T'}\). 
We follow the 
aforementioned procedure for 
reference speech to get tensor \(\bm{d_r}\) of shape \(n \times T_r\). But for the mixed 
speech, instead of directly following the procedure, we first concatenate it with 
the reference speech to get \(s' = [s_r, s_m, s_r] \in R^{(T^r+T'+T^r)}\). Then we use this speech 
as input for the encoder, obtaining output \(\bm{d'}\) of shape \(n \times (T_r+T+T_r)\) where \(T\) 
denotes the length of output by directly passing the mixed speech without concatenation.
